---
title: "p8105_hw1_xl3495"
output: github_document
---

```{r}
#load the dataset
data("penguins", package = "palmerpenguins")
```

# Problem 1

```{r}
row = nrow(penguins)
col = ncol(penguins)
flipper_length = penguins$flipper_length_mm
mean_flipper_length = mean(flipper_length,na.rm = TRUE)
```
The `penguins` dataset has 8 variables in total and the size of the dataset is `r row * col` (_nrow_:`r row`; _ncol_:`r col`). The variables basically describes features of penguins such as `species`(Adélie, Chinstrap and Gentoo), `body_mass`, `sex`(male/female) and `year`. Also, variables like `bill_length_mm` and `bill_depth_mm` describes the bill length and depth in millimeters separately. The variable `flipper_length_mm` is an integer denoting flipper length in millimeters, with `r mean_flipper_length`mm in average.

The scatterplot of `flipper_length_mm (y)` vs `bill_length_mm (x)`:

```{r warning = FALSE}
#import library
library(tidyverse)
#create a scatteplot
plot = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species))+geom_point()
# Save as a JPEG
ggsave("scatter_plot.jpeg", plot = plot)
```
```{r echo = FALSE,warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species))+geom_point()
```

# Problem 2

```{r}
#create a data frame
#library(tidyverse) already loaded
df = tibble(
  norm_samp = rnorm(10),
  vec_logical = norm_samp > 0,
  vec_char = c("apples",
               "bananas",
               "chocolates",
               "daikon radish",
               "eggplant",
               "fudge",
               "grapes",
               "honeydew_melon",
               "ice_cream",
               "jicama"),
  vec_factor = factor(c("fruit",
                        "fruit",
                        "snack",
                        "vegetable",
                        "vegetable",
                        "snack",
                        "fruit",
                        "fruit",
                        "snack",
                        "vegetable"
                        ))
)


```
## Mean of Each Variable
```{r}
mean_norm_samp = mean(df %>% pull(norm_samp))
```
This returns a mean of 10 random samples from a standard normal distribution. Mean: `r mean_norm_samp`, which is a numeric value.
```{r}
mean_vec_logical = mean(df %>% pull(vec_logical))
```
This returns a mean of logical factor. Here, `TRUE` is coerced to `1` and `FALSE` is coerced to `0`. Mean: `r mean_vec_logical`, which is a numeric value. This way, it is convenient to determine the proportion of `TRUE` values.
```{r}
mean_vec_char = mean(df %>% pull(vec_char))
```
This returns `NA` with the warning above.
```{r}
mean_vec_factor = mean(df %>% pull(vec_factor))
```
This returns `NA` with the warning above.

```{r eval = FALSE}
#Trying to coerce with as.numeric() function
as.numeric(df %>% pull(vec_logical))
as.numeric(df %>% pull(vec_char))
as.numeric(df %>% pull(vec_factor))
```
Logical and factor variables can be coerced to numeric values while character variable cannot (`NA`s introduced by coercion for character variables). I think this is because logical and factor variables has the meaning of **categories** or **levels**, while the meaning of character variables differ from each other. However, mean can be only calculated with numeric values, so the character variables have no mean, returning nothing but `NA`s.



